Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-06-21 ms.tex
Not really a horizon distance

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ and $h_{\pi/2}$. For nonprecessing systems, $h = h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. In other words, $h_{\pi/2}(\omega) = i h_0(\omega)$ for all $\omega$. This linear combination isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform,
%
\begin{eqnarray}\label{eq:full-signal-model}
	\fl h_i(\omega; \boldsymbol\theta) &=& e^{-i\omega t_\oplus}\frac{D_{1,i}}{D_\mathrm{L}}
	\left(\begin{array}{cc}
		F_{+,i}(\alpha, \delta, t_\oplus) \\
		F_{\times,i}(\alpha, \delta, t_\oplus)
	\end{array}\right)^\intercal
	\left(\begin{array}{cc}
		\cos{2\psi} & -\sin{2\psi} \\
		\sin{2\psi} & \cos{2\psi}
	\end{array}\right)
	\left(\begin{array}{cc}
		\frac{1}{2}\left(1+u^2\right) & 0 \\
		0 & u
	\end{array}\right) \nonumber\\\fl &\cdot&
	\left(\begin{array}{cc}
		\cos{2\phi_c} & -\sin{2\phi_c} \\
		\sin{2\phi_c} & \cos{2\phi_c}
	\end{array}\right)
	\left(\begin{array}{cc}
		1 \\
		i
	\end{array}\right) h(\omega; \boldsymbol\theta_\mathrm{in}).
\end{eqnarray}
%
This linear combination matches the conventions used in \cite{PhysRevD.83.084002}, and is the frequency-domain equivalent of their Equation~(2.8). The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial horizon distance for detector $i$,
%
\marginpar{This isn't what we usually call the horizon distance; the horizon distance is where face-on inspirals produce SNR=8.}%
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,\mathrm{d}\omega.
\end{equation}

>>>>

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ and $h_{\pi/2}$. For nonprecessing systems, $h = h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. In other words, $h_{\pi/2}(\omega) = i h_0(\omega)$ for all $\omega$. This linear combination isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform,
%
\begin{eqnarray}\label{eq:full-signal-model}
	\fl h_i(\omega; \boldsymbol\theta) &=& e^{-i\omega t_\oplus}\frac{D_{1,i}}{D_\mathrm{L}}
	\left(\begin{array}{cc}
		F_{+,i}(\alpha, \delta, t_\oplus) \\
		F_{\times,i}(\alpha, \delta, t_\oplus)
	\end{array}\right)^\intercal
	\left(\begin{array}{cc}
		\cos{2\psi} & -\sin{2\psi} \\
		\sin{2\psi} & \cos{2\psi}
	\end{array}\right)
	\left(\begin{array}{cc}
		\frac{1}{2}\left(1+u^2\right) & 0 \\
		0 & u
	\end{array}\right) \nonumber\\\fl &\cdot&
	\left(\begin{array}{cc}
		\cos{2\phi_c} & -\sin{2\phi_c} \\
		\sin{2\phi_c} & \cos{2\phi_c}
	\end{array}\right)
	\left(\begin{array}{cc}
		1 \\
		i
	\end{array}\right) h(\omega; \boldsymbol\theta_\mathrm{in}).
\end{eqnarray}
%
This linear combination matches the conventions used in \cite{PhysRevD.83.084002}, and is the frequency-domain equivalent of their Equation~(2.8). The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial distance at which detector $i$ would register SNR=1 for an optimally oriented binary (face\nobreakdashes-on, and in a direction perpendicular to the interferometer's arms),
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,\mathrm{d}\omega.
\end{equation}
